---
title: "Chapter 3: Data Visualization"
author: "Brianna Cabrera"
date: "9/24/19"
output: github_document
---

##3.1.1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment="")
library(tidyverse)
```

##3.2.2

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```

##3.3.4 Exercises

```{r}
ggplot(data = mpg)
```
The code ran, but there is no graph.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = hwy, y = cyl))
```

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = class, y = drv))
```
This graph doesn't give us any useful information. DRV is not a useful variable to measure the different classes of cars by.

##3.3.1 Exercises
1. The "color"blue"" part of the code needs to be in its own parentheses and not next to the x and y variables.
2. 
```{r}
?mpg
```
The categorical variables include the model, trans, drv, fl, and class. The continuous variables include displ, year, cly, cty, and hwy. If you run "mpg" in a code chunk you are able to view all this information.

3.
```{r}
ggplot(data = mpg,mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping = aes(color=class))
```
